---
title: "Analytics with R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Installation

```{r}
install.packages('gdata')
install.packages('dplyr')
library(gdata)
library(dplyr)
```


Check and set your working directory

```{r}
getwd()
setwd("Users/hollyemblem/Projects/analysis - with - r")
```

Read in your Analytics file
```{r}
analytics <- read.csv("analytics.csv",stringsAsFactors = FALSE,strip.white=TRUE)
View(analytics)
```

We use strings as factors = FALSE, as our first column are not factor variables. To find out more about why we should set this, see here: https://simplystatistics.org/2015/07/24/stringsasfactors-an-unauthorized-biography/

Now we can update our final column to contain 'Total' on the last row:

```{r}
analytics[8,1] <- "Total"
```


From here, we can easily calculate the mean and median of, say, sessions:

```{r}
analytics %>% filter(Day.Index !="Total", (!is.na(Sessions))) %>% summarise(mean_visits =(mean(as.numeric(Sessions))))
```


We can also easily create a bar chart:

```{r}
ggplot(data=subset(analytics,Day.Index != "Total"),aes(x=Day.Index, weight=Users)) +  geom_bar()
```

